Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
add intro
Iterating on Thm 27

We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $w \in \reals^2$ such that $\langle v_j, w \rangle = B_{ij}$.

Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
\jessie{Left off here before the reading group}
In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
\end{proof}

>>>>

We then want to show there is no $V\in \reals^{5\times 2}$ so that for all $i \in \{1, 2, \ldots, 5\}$ that $(V, B_i)$ is a tight H-rep, following from Definition~\ref{def:d-construction}.
Therefore, we show that there is no $V \in \reals^{5 \times 2}$ such that $S_i := \{w : Vw \leq B_i \}$ is nonempty and for $j = 1, \ldots, 5$, there is a $x \in \reals^2$ such that $\langle v_j, x \rangle = B_{ij}$.

\jessie{This is from the PDF notes...}
In fact, in order for the H-reps to be tight, we must observe that for all $i, j$, the $\max_{x \in S_i} \langle v_j, x \rangle = -1$ if $i = j$ and $1$ otherwise.
For all $i,j$, we denote $x_{ij}$ so that $\langle v_i, x_{ij} \rangle = \langle v_j, x_{ij} \rangle = 1$.
Numbering the normals clockwise, modulo 5, then for all $i$, we need $\langle v_i, x_{i+1, i+2} \rangle \leq -1$ and $\langle v_i, x_{i-1, i-2} \rangle \leq -1$.

Focusing on $v_1$, we know that $\langle v_1, x_{23} \rangle \leq -1$ and $\langle v_1, x_{45} \rangle \leq -1$ if and only if $\theta_{13} = \theta_{12} + \theta_{23} \geq 180^o$  and $\theta_{41} = \theta_{51} + \theta_{45} \geq 180^o$.
These statements are only jointly true if $\theta_{13} = \theta_{41} = 180^o$.
However, the only way to reach this conclusion is if $\theta_{34} = 0^o$, and as the vectors are all unit vectors, we conclude $v_3 = v_4$.
We can see that this scenario contradicts the tightness of the H-reps $(V, B_3)$ and $(V, B_4)$.
As $S_3 = \{w : Vw \leq (1,1,-1,1,1)^T\}$, if $v_3 = v_4$, then the polytope $S_3$ is a line in $\reals^2$ and the constraint $\langle v_1, x \rangle = 1$ is not true for any $x \in S_3$.
Therefore, there is some $i$ such that $(V,S_i)$ is not a tight H-representation.
Thus, the cell $B^{(abs)}$ does not have a $2$-construction, and the property is not $2$-embeddable.

%Similarly, we can see that $\langle v_2, x_{34} \leq -1$ and $\langle v_2, x_{15} \rangle \leq -1$ if and only if $v_4 = -v_2$.
%Therefore, we know that $\theta_{24} = 180^o = \theta_{23} + \theta_{34} = \theta_{12} + \theta{51} + \theta_{45}$
%
%Now, in order for $\langle v_5, x_{12} \leq -1$ and $\langle v_2, x_{34} \rangle \leq -1$ to hold, 
%
%Therefore, for all $v_i$, there must be some $v_j = -v_i$ in $V$.
%
%Consider $V = (v_1, \ldots, v_5)^T$ and, without loss of generality, let $v_1 = (0,1)$.
%
%
%We assert that $v_2 := -v_1$ must be in the set of normals.
%This can be seen since, for the normals $v_1$ and $v_2$, then angle $\theta_{12}$ between the two normals must be $180^o$.
%Since we have $5$ normals, the angle between normals $v_1$ and $v_2$ can be written $\theta{12} = \theta{1i} + \theta_{i2}$.
%(One direction of the angles must have some $v_i$ between $v_1$ and $v_2$.)
%If $\theta_{1i} \leq 90^o$, then $\theta_{1i} + \theta_{i2} \geq 180^o$ in order for there to be a $w$ such that $\langle v_2, w \rangle = 1$.
%
%
%\jessie{Left off here before the reading group}
%In order for the H-rep to be tight, then for all $v_j$ for $j > 1$, $\langle v_j, w \rangle = 1$ and $w = (x, -1)$.
%Observe that a line (here, a facet of the polytope) in $\reals^2$ cannot be nonredundantly bounded by $3$ points.
%This suggests that, in order for $(V,B_1)$ to be tight, at least two facets must both intersect $\langle v_1, w \rangle$ at the same point.
%However, since each $v_j$ must be a unit normal and the facets must intersect at the same point $w$, $\langle v_j, w \rangle = \langle v_k, w \rangle$ for $j \neq k$ if and only if $v_j = v_k$.
%However, if $v_j = v_k$, then the representations $(V, B_j)$ and $(V, B_k)$ will not be tight. 
%This can be seen as there will be no $w \in \{ w: \langle v_j, w \rangle = 1 \}$ that is also on the face $\{w : \langle v_j, w \rangle =-1 \} = \{w : \langle v_k, w \rangle = -1\}$, and vice versa.
%Therefore, there is no set of normals $V \in \reals^{5\times 2}$ so that $\{w : Vw = B_i\}$ is tight for all $v_j$ and $B_i$.
%Therefore, since there is no $2$-construction of abstain(1/2) on $5$ outcomes, we conclude it is not $2$-embeddable.
%\jessie{Weird to think of it this way after drawing so many pictures, but this might be more elegant if it's close.}
\end{proof}
